Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy

### 2024-09-17 si.tex
more edits

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/changedelta.png}
	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
	\label{fig:chgdelta}
\end{figure}
\section{Evaluating impact of inhomogeneity on HDFG output}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated using Contour integration.
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/corr_contour.png}
	\caption{Poles (blue dots) and contours (black line) used to evaluate \autoref{generalcontour} for (a) anti-correlated and (b) correlated modes.} 
	\label{fig:contours}
\end{figure}
\subsection{Anti-correlated Modes}
For anti-correlated modes ($c = -1$), the poles ($\xi_k$) are situated in the complex plane as shown in \autoref{fig:contours}a.
Since \autoref{generalcontour} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
In other words, we can choose the contour which wraps around the least number of poles.
For c = -1, there are four poles: $\pm i \sigma, \Delta_{ga}, \Delta_{ba}$. 
The contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{generalcontour} in the upper half of the complex plane for the case of anti-correlated modes, as it contains the least number of poles.
Using the residue theorem, we see
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} (\xi - i \sigma)\\
			&= 2 \eta_{ijkl} \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi}\\
			&= 2\eta_{ijkl} \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} - i\sigma}\\
			&= \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma\right)\left(\Delta_{ba}-i \sigma\right)}\\
		\end{split}
	\end{equation}
\end{widetext}

\subsection{Correlated Modes}
For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
It is clear that no matter which contour is chosen, there is a contribution from either $\Delta_{ba}$ or $\Delta_{ga}$. 
For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles are $\{-i\sigma, \Delta_{ga}\}$.
We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can \textit{also} be obtained by evaluating the contour which wraps around the poles $\{i\sigma, -\Delta_{ba}\}$. 
Nevertheless, we choose the contour as drawn in \autoref{fig:contours}b.
Since the $\xi_k$ are nondegenerate, we see
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} + \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi + i \sigma\right) \\ 
			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow \Delta_{ga}} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi - \Delta_{ga}\right)\\
			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}} \frac{1}{\Delta_{ba} - i\sigma} \right) - 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ga} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
			&= -\frac{\eta_{ijkl}}{\Delta_{ga} + i \sigma} \left(\frac{1}{\Delta_{ba} - i \sigma} + \frac{2i\sigma}{(\Delta_{ga} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)\\
		\end{split}
	\end{equation}
\end{widetext}
Generally, when starting from the ground state, non-parametric spectroscopies line-narrow correlated modes, and parametric spectroscopies line-narrow anti-correlated modes. \cite{Dick83_1, RN425}

>>>>

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/changedelta.png}
	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
	\label{fig:chgdelta}
\end{figure}
\section{Evaluating impact of inhomogeneity on HDFG output}
In this section, the integral
\begin{equation}\label{generalcontour}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
	\end{split}
\end{equation}
is evaluated using Contour integration.

\subsection{Anti-correlated Modes}
For anti-correlated modes ($c = -1$), the poles ($\xi_k$) are situated in the complex plane as shown in \autoref{fig:contours}a.
Since \autoref{generalcontour} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
In other words, we can choose the contour which wraps around the least number of poles.
For c = -1, there are four poles: $\pm i \sigma, \Delta_{ga}, \Delta_{ba}$. 
The contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{generalcontour} in the upper half of the complex plane for the case of anti-correlated modes, as it contains the least number of poles.
Using the residue theorem, we see
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} (\xi - i \sigma)\\
			&= 2 \eta_{ijkl} \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi}\\
			&= 2\eta_{ijkl} \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} - i\sigma}\\
			&= \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma\right)\left(\Delta_{ba}-i \sigma\right)}\\
		\end{split}
	\end{equation}
\end{widetext}

\subsection{Correlated Modes}
For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
It is clear that no matter which contour is chosen, there is a contribution from either $\Delta_{ba}$ or $\Delta_{ga}$. 
For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles are $\{-i\sigma, \Delta_{ga}\}$.
We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can \textit{also} be obtained by the contour that wraps around the poles $\{i\sigma, -\Delta_{ba}\}$. 
Nevertheless, we choose the contour as drawn in \autoref{fig:contours}b.
Since the $\xi_k$ are nondegenerate, we see
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} + \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi + i \sigma\right) \\ 
			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow \Delta_{ga}} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi - \Delta_{ga}\right)\\
			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}} \frac{1}{\Delta_{ba} - i\sigma} \right) - 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ga} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
			&= -\frac{\eta_{ijkl}}{\Delta_{ga} + i \sigma} \left(\frac{1}{\Delta_{ba} - i \sigma} + \frac{2i\sigma}{(\Delta_{ga} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)\\
		\end{split}
	\end{equation}
\end{widetext}
Generally, when starting from the ground state, non-parametric spectroscopies line-narrow correlated modes, and parametric spectroscopies line-narrow anti-correlated modes. \cite{Dick83_1, RN425}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=6.675in]{figures/corr_contour.png}
	\caption{Poles (blue dots) and contours (black line) used to evaluate \autoref{generalcontour} for (a) anti-correlated and (b) correlated modes.} 
	\label{fig:contours}
\end{figure}
